Spitzer Sgr target selection

### 2013-11-09 text/notes/spitzer_target_selection/spitzer_sgr.tex
fixed koposovs flipped beta

\section{An overview of the sample}
\begin{itemize}
	\item Three clumps (29 stars total) along the leading tail (sampling in orbital phase);
	\item a clump of 8 stars selected to be associated with the bifurcated part of the stream;
	\item a clump of 10 stars selected to be associated with the nearby part of the trailing arm;
	\item 16 stars selected from the trailing arm with $\Lambda$ $<$ 180.
\end{itemize}
Though the bifurcated stream targets and nearby trailing targets are selected based on distance, radial velocity, and $B$, it is possible that they will not reveal anything (still interesting) -- these two components only account for $\sim$15\% of the time, so we think this is acceptable.

@@

The remaining sample consists of 66 RR Lyrae, with a total required integration time of $\sim$280 hr and is shown in Figure~\ref{fig:final_sample} (green), along with other RR Lyrae that meet the above cuts but are not in the chosen clumps (red), overlaid with the LM10 particles.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{L_vs_B.pdf}
\caption{ $\Lambda$ vs. $B$ for LM10 particles (black) and selected particles (excluding the nearby trailing stars, for now). Blue are selected to not be associated with the bifurcation, green are the clump selected to be associated with the bifurcation. }\label{fig:LB}
\end{center}
\end{figure}

>>>>

\section{An overview of the sample}
\begin{itemize}
	\item Three clumps (31 stars total) along the leading tail (sampling in orbital phase);
	\item a clump of 8 stars selected to be associated with the bifurcated part of the stream;
	\item a clump of   stars selected to be associated with the nearby part of the trailing arm;
	\item 16 stars selected from the trailing arm with $\Lambda$ $<$ 180.
\end{itemize}
Though the bifurcated stream targets and nearby trailing targets are selected based on distance, radial velocity, and $B$, it is possible that they will not reveal anything (still interesting) -- these two components only account for $\sim$15\% of the time, so we think this is acceptable.

@@

The remaining sample consists of 65 RR Lyrae, with a total required integration time of $\sim$280 hr and is shown in Figure~\ref{fig:final_sample} (green), along with other RR Lyrae that meet the above cuts but are not in the chosen clumps (red), overlaid with the LM10 particles.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{without_near_trailing_LB.pdf}
\caption{ $\Lambda$ vs. $B$ for LM10 particles (black) and selected particles (excluding the nearby trailing stars, for now). Blue are selected to not be associated with the bifurcation, green are the clump selected to be associated with the bifurcation. }\label{fig:LB}
\end{center}
\end{figure}
